Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
10 pages

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular use of multiple websites to accomplish tasks, examples of which including: shopping (including food, consumer electronics, hotels and flights), choosing restaurants, job-seeking, selecting a university, seeking recipes, and finding answers to technical problems.  When beginning a task, it was common for participants to use Google to discover several related websites, which would then be used in different ways depending on the task at hand. For shopping-oriented tasks, balancing price, quality and speed of delivery was the main aim.  For product reviews, single sources were not trusted due to possible bias and incomplete feature coverage.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To provide a full coverage of information, websites of different types were used, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.

%\subsubsection{Question 2: Process Used to Organise a Large Social Event}
Participants said they would organise a large social event by first conferring with friends about their ideas, preferences and recommendations.  They selected venues, locations, restaurants and activities through a number of sources: their own prior experience, friends' recommendations, searching Google maps, dedicated reviews sites (such as Yelp for restaurants), and through web search.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web, or organised carpools.  When organising an event, the weather was not that important because they did not trust the accuracy of predictions.  
% Also, friends' preferences in price and food choices were not seen as a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.

@@

Our study had several limitations.  First, the small sample size of our study (20 participants) meant that we could not confirm some of the effects observed with statistical significance.  Second, giving participants a time limit of 10 minutes on trials may have affected the strategies they used to make their choices.  For this reason, in our follow-up study, we will try to give some participants unlimited time on tasks of similar complexity.  A second departure from a realistic task was the way in which we pre-determined the data sources for participants to use.  We did this in order to focus participants' efforts on looking at and working with their choices, rather than retrieving it.  However, as supporting effective retrieval and serendipitous discovery will be important for DP to be useful in practice, we plan to look at supporting these stages in the future. 
% \subsection{Integration Limitations}

>>>>

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular use of multiple websites to accomplish tasks, examples of which including: shopping (food, consumer electronics, hotels and flights), choosing restaurants, job-seeking, selecting a university, seeking recipes, and finding answers to technical problems.  When beginning a task, it was common for participants to use Google to discover several related websites, which would then be used in different ways depending on the task at hand. For shopping-oriented tasks, balancing price, quality and speed of delivery was the main aim.  For product reviews, single sources were not trusted due to possible bias and incomplete feature coverage.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To provide a full coverage of information, websites of different types were used, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.

%\subsubsection{Question 2: Process Used to Organise a Large Social Event}

Participants said they would organise a large social event by first conferring with friends about their ideas, preferences and recommendations.  They selected venues, locations, restaurants and activities through a number of sources: their own prior experience, friends' recommendations, searching Google maps, dedicated reviews sites (such as Yelp for restaurants), and through web search.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web, or organised carpools.  
%When organising an event, the weather was not that important because they did not trust the accuracy of predictions.  Also, friends' preferences in price and food choices were not seen as a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.

% old:
% Participants said they would organise a large social event by first conferring with friends about their ideas, preferences and recommendations.  They selected venues, locations, restaurants and activities through a number of sources: their own prior experience, friends' recommendations, searching Google maps, dedicated reviews sites (such as Yelp for restaurants), and through web search.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web, or organised carpools.  When organising an event, the weather was not that important because they did not trust the accuracy of predictions.  Also, friends' preferences in price and food choices were not seen as a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.\looseness=-1

@@

Our study had several limitations.  First, the small sample size of our study (20 participants) meant that we could not confirm some of the effects observed with statistical significance.  Second, giving participants a time limit of 10 minutes on trials may have affected the strategies they used to make their choices.  For this reason, in our follow-up study, we will give some participants unlimited time on tasks of similar complexity.  A second departure from a realistic task was the way in which we pre-determined the data sources for participants to use.  We did this in order to focus participants' efforts on looking at and working with their choices, rather than retrieving it.  However, as supporting effective retrieval and serendipitous discovery will be important for DP to be useful in practice, we plan to look at supporting these stages in the future. 
% \subsection{Integration Limitations}
